Depression and suicidality as costly signals of need

### 2021-04-22 Paper.rmd
Working on introduction

### alternate start

Conflicts of interest are ubiquitous among living things, even among closely related individuals. The result of this is often situations in which one individual benefits greatly from another while providing little benefits or substantial costs in return. In species which rely heavily on cooperation, like our own, this often manifests in substantial outward conflict about levels of investment the harm an individual is inflicting on another.

@@

The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India). After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstatus['Married']` of whom were married or in a long-term relationship, `r relstatus['Divorced']` who were divorced, `r relstatus['Single']` who were single, and `r relstatus['Widowed']`. The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`). For the number of participants in each condition, see Table \@ref(tab:conditions). For summary statistics, see Table \@ref(tab:sumtab). For the distributions of participants by age, income, and nationality, see Figure \@ref(fig:socioeconomic).

>>>>

Conflicts of interest are ubiquitous, even among closely related individuals. In species that rely heavily on cooperation, like our own, conflicts can arise over the level of investment in a cooperative endeavor and the division of the resulting benefits. In many such cases, individuals who are dissatisfied with their social partners would seek other partners. In many other cases, however, it would be difficult or impossible to switch partners. A wife who is dissatisfied with her husband's investment in their new infant, for example, would not easily find a different husband to invest in that infant, nor could the husband easily find a different wife to invest in that infant. An adolescent who is dissatisfied with her parent's investment in her would not easily find other parents who are willing to invest more, nor could parents easily produce another adolescent. In many cooperative endeavors central to human biological fitness, each party has monopoly power over the benefits they bring to the endeavor -- no one is easily replaced.

Conflict resolution therefore requires that the levels of investment in and division of benefits from the endeavor

@@

The study was started by N=`r nrow(signaling2020)` participants who clicked the link to Qualtrics (`r nationT0['American']` US and `r nationT0['Indian']` India). After removing participants who did not finish the survey, failed attention checks, or moved through the study at an unrealistic pace (N=`r removed`, `r removed_pct`%), our final sample was N = `r nrow(d)` (`r nationT1['American']` US and `r nationT1['Indian']` India), with `r sexT1['Male']` males and `r sexT1['Female']` females, `r relstats['Married']` of whom were married or in a long-term relationship, `r relstats['Divorced']` who were divorced, `r relstats['Single']` who were single, and `r relstats['Widowed']`. The median number of participants per condition was `r median(n_cond)` (min=`r min(n_cond)`, max=`r max(n_cond)`). For the number of participants in each condition, see Table \@ref(tab:conditions). For summary statistics, see Table \@ref(tab:sumtab). For the distributions of participants by age, income, and nationality, see Figure \@ref(fig:socioeconomic).
